---
title: "gender"
output: html_document
date: '2022-07-10'
---

```{r}
library(dplyr)
library(ggplot2)
library(ggmosaic)
```

#1 Participation ID for participants who took part in all three surveys

```{r}
all_three=(da34375.0001) %>% filter(FU1_MARKER=="(1) Completed Wave",FU2_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% select(SU_ID)

all_three

```

#2 Participation ID for participants who took part in baseline and first follow up survey

```{r}
first_two=(da34375.0001) %>% filter(FU1_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% select(SU_ID)

first_two
```

#3 Participation ID for participants who took part in baseline and second follow up.

```{r}
first_last=(da34375.0001) %>% filter(FU2_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% mutate(participation=c("first and last"))%>%select(SU_ID,participation)

first_last
```

#4 Creating a newdata set consisting of all columns from the original dataset along with a new "participation" column which tracks if the participant participated in "all three","first and last", "first two" or NA.

```{r}
df <- da34375.0001 %>% 
mutate(participation = case_when(
  
  ((FU2_MARKER=="(1) Completed Wave") & (BL_MARKER=="(1) Completed Wave")&(FU1_MARKER=="(1) Completed Wave")) ~ "all three",

    ((FU2_MARKER=="(1) Completed Wave") & (BL_MARKER=="(1) Completed Wave")) ~ "first and last",
   
    
    
    ((BL_MARKER=="(1) Completed Wave")&(FU1_MARKER=="(1) Completed Wave")) ~ "first two"

))

df
```

#5 Check to see code #4 works accurately

```{r}
new<-df%>%select(participation,SU_ID,BL_MARKER,FU1_MARKER,FU2_MARKER)
new
```

#6 Filtering for "participation" column with"all three","first and last", "first two"

```{r}
new_dataset<- df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SU_ID, SEX_DB,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)%>%filter(SEX_DB=="(1) Male" & BL_R_GENDER=="(2) Female")
 
new_dataset

```

#filtering m to f and f to m participants

```{r}
new_df <- (da34375.0001) %>% 
mutate(transition = case_when(
  
  ((SEX_DB=="(1) Male") & (BL_R_GENDER
=="(2) Female")) ~ "MtoF",

   ((SEX_DB=="(2) Female") & (BL_R_GENDER
=="(2) Male")) ~ "FtoM",
 
   
    (TRUE)~ "No"
))

#new_df%>%select(transition,SU_ID)
#%>%filter(transition=="MtoF"|transition=="FtoM")
new_df%>%select(transition)%>%filter(transition!="No")
```

```{r}
new_dataset_1<- df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SEX_DB,SU_ID)%>%filter(SEX_DB!="(1) Male" & SEX_DB!="(2) Female")
 
new_dataset_1

```

```{r}
new_dataset_2<- df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SU_ID,SEX_DB)%>%filter(SEX_DB=="(1) Male")

new_dataset_2
```

```{r}
new_dataset_3<- df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SU_ID,SEX_DB)%>%filter(SEX_DB=="(2) Female")

new_dataset_3
```

```{r}
filtered_dataset<- df%>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SU_ID,SEX_DB,BL_R_GENDER,BL_GMSLEADR,BL_GMSLDACT,BL_FRNNCOLL,BL_GLEADER, BL_UDIFFFRN,BL_SESATISF,BL_LCGETAHD,BL_SEESTMWO,BL_SEDOWELL,BL_SEUSELES,BL_SENOGOOD,BL_LCPLANSW,BL_COMDEGRE,BL_UDIFFSCW,BL_UDIFFTIM,BL_UNDSOSTU, BL_SELFGOOD,BL_UDIFFFRN,BL_UNDSFAC,BL_UNDSOSTU,BL_LCNECNTR,BL_HSMATHYR,BL_HSSCIEYR,FU1_GMSLEADR,FU1_GLEADER,FU1_R_GENDER,FU1_APLYGRAD,FU1_GMSLDACT,FU1_UCULTURE,FU1_GLEADER,FU1_RGRPSSUP,FU1_POLPROG,FU1_DIFFSCHW,FU1_PPOTHR,FU1_DIFFSCHW,FU1_SOCDISCR,FU1_FACINAPP,FU1_SELFGOOD,FU1_LCNECNTR,FU1_SEESTMWO,FU1_SEDOWELL,FU1_LCGETAHD,FU1_AENOTWEL,FU1_AEMAKCOL,FU1_SESATISF,FU1_SEUSELES,FU1_SENPROUD,FU2_NOGRNOSC,FU2_GMSLDACT,FU2_HLTHINSR,FU2_SATCOWRK,FU2_OPPJOB,FU2_COMDIVRS,FU2_PNSADJUS,FU2_DESTLEAD,FU2_POSCULT,FU2_DIFFVIEW,FU2_BULDCOAL,FU2_VOTEELEC,FU2_PROMEQIT,FU2_R_GENDER,FU2_GMSLEADR)
#%>%filter(SEX_DB=="(2) Female")

filtered_dataset
```

# Not all male or female. Missing values.

```{r}
new_dataset_7<- df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SEX_DB,SU_ID,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)%>%filter((SEX_DB=="(1) Male"&BL_R_GENDER=="(1) Male"&FU1_R_GENDER=="(1) Male"&FU2_R_GENDER=="(1) Male")|(SEX_DB=="(2) Female"&BL_R_GENDER=="(2) Female"&FU1_R_GENDER=="(2) Female"&FU2_R_GENDER=="(2) Female"))
 
new_dataset_7

```

```{r}
l<-df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SEX_DB,SU_ID,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)

new_df<-anti_join(l,new_dataset_7,by="SU_ID")
new_df

```

#Visualizaton

```{r}
new_df <- df %>% 
mutate(unknown_sex = case_when(
  
  ((SEX_DB!="(1) Male") & (SEX_DB!="(2) Female"))~ "YES",
   
   TRUE~"NO"))

new_df

```

```{r}
missing<- new_df %>%filter(participation=="all three"|participation=="first and last"|participation=="first two")%>%select(SU_ID,SEX_DB,BL_GMSLEADR,BL_GMSLDACT,BL_FRNNCOLL,BL_GLEADER,BL_UDIFFFRN,BL_SESATISF,BL_LCGETAHD,BL_SEESTMWO,BL_SEDOWELL,BL_SEUSELES,unknown_sex,BL_SENOGOOD,BL_LCPLANSW,BL_COMDEGRE,BL_UDIFFSCW,BL_UDIFFTIM,BL_UNDSOSTU, BL_SELFGOOD)

missing
```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SESATISF), fill = BL_SESATISF, 
                  conds = product(unknown_sex))) +
  labs(title='(unknown sex |On the whole I am
  satisfied with myself.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SESATISF), fill = BL_SESATISF, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | On the whole I am 
  satisfied with myself.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_GLEADER), fill = BL_GLEADER, 
                  conds = product(unknown_sex))) +
  labs(title='(unknown sex | During this school year,
       have you held a campus leadership position?)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_GLEADER), fill = BL_GLEADER, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | During this school year, 
       have you held a campus leadership position?)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_UDIFFFRN), fill = BL_UDIFFFRN, 
                  conds = product(unknown_sex))) +
  labs(title='(unknown sex | How difficult did
       you find making friends?)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_UDIFFFRN), fill = BL_UDIFFFRN, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | How difficult did
       you find making friends?)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_FRNNCOLL), fill = BL_FRNNCOLL, 
                  conds = product(unknown_sex))) +
  labs(title='(unknown sex | Most of my 
       friends are not in college?)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_FRNNCOLL), fill = BL_FRNNCOLL, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | Most of my 
  friends are not in college)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_LCGETAHD), fill = BL_LCGETAHD, 
                  conds = product(unknown_sex))) +
  labs(title='(unknown sex | Every time I try
       to get ahead, something or
       somebody stops me.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_LCGETAHD), fill = BL_LCGETAHD, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | Every time I try 
       to get ahead, something or 
       somebody stops me.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SEESTMWO), fill = BL_SEESTMWO, 
                  conds = product(unknown_sex))) +labs(title='(Unknown Sex | I feel I am
  a person of worth, the equal of other people.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SEESTMWO), fill = BL_SEESTMWO, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth | I feel I am a person of worth,
  the equal of other people.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SEDOWELL), fill = BL_SEDOWELL, 
                  conds = product(unknown_sex))) +
  labs(title='f(unknown sex |I am able to do
  things as well as most other people.)')

```

```{r}
ggplot(data = missing) +
  geom_mosaic(aes(x=product(BL_SEDOWELL), fill = BL_SEDOWELL, 
                  conds = product(SEX_DB))) +
  labs(title='(Sex at birth |I am able to do 
  things as well as most other people.)')

```

```{r}
ggplot(data = missing,aes(x=unknown_sex,y=BL_GMSLDACT))+geom_point()

```

```{r}
ggplot(data = missing,aes(x=SEX_DB,y=BL_GMSLDACT))+geom_point()

```

<https://www.cedars-sinai.org/newsroom/most-gender-dysphoria-established-by-age-7-study-finds/#>:\~:text=All%20of%20the%20participants%20were,gender%20dysphoria%20by%20age%207.

https://www.scottishtrans.org/wp-content/uploads/2013/03/trans_mh_study.pdf

https://bmcpublichealth.biomedcentral.com/articles/10.1186/s12889-020-8228-5

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6234844/

https://www.sciencedirect.com/science/article/pii/S0277953621004755


most likely: second follow up is missing, sex_db, se least likely: if either the first follow up or baseline is missing with sex_db intact and shows consistent pattern might: sex_db-b, baseline-b, 1st follow-c, 2nd follow-a, sex_db & baseline-a, sex_db & 1st_follow=c, sex_db & 2nd_follow-a,baseline & 2nd follow-a, baseline & 1st follow, 1st follow & 2nd follow, sex_db & baseline & 1st follow-c,baseline & 1st follow & 2nd follow-a, sex_db & 1st follow & 2nd follow-c,sex -db & 2nd follow & baseline-c.

```{r}
new_df1 <- (filtered_dataset) %>% 
mutate(weights = case_when(
  
  ((SEX_DB=="(3) Unknown") & (is.na(BL_R_GENDER)
) & (FU1_R_GENDER=="(2) Female")& (FU2_R_GENDER=="(2) Female")) ~ "Most",

((SEX_DB=="(3) Unknown") & (is.na(BL_R_GENDER)) & (FU1_R_GENDER=="(1) Male")& (FU2_R_GENDER=="(1) Male")) ~ "Most",

   ((SEX_DB=="(3) Unknown") & (is.na(FU1_R_GENDER)) &(BL_R_GENDER=="(1) Male")&(FU2_R_GENDER=="(1) Male")) ~ "Least",

 ((SEX_DB=="(3) Unknown") & (is.na(FU1_R_GENDER)) &(BL_R_GENDER=="(2)Female")&(FU2_R_GENDER=="(2) Female")) ~ "Least",

((SEX_DB=="(3) Unknown") & (is.na(FU2_R_GENDER))& (FU1_R_GENDER=="(1)Male")&(BL_R_GENDER=="(1)Male")) ~ "Most",

((SEX_DB=="(3) Unknown") & (is.na(FU2_R_GENDER))& (FU1_R_GENDER=="(2)Female")&(BL_R_GENDER=="(2)Female")) ~ "Most",


((is.na(BL_R_GENDER)) & (is.na(FU2_R_GENDER)) & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1)Male")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU2_R_GENDER)) & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2)Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(1) Male")&(FU2_R_GENDER=="(1) Male")) ~ "Least",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(2)Female")&(FU2_R_GENDER=="(2) Female")) ~ "Least",
 
 
((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(2) Female")&(BL_R_GENDER=="(2) Female")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(1) Male")&(BL_R_GENDER=="(1) Male")) ~ "Most",
 
 
((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(BL_R_GENDER=="(1) Male")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(BL_R_GENDER=="(2) Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(FU2_R_GENDER=="(2) Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(FU2_R_GENDER=="(1) Male")) ~ "Most",

 
 ((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (is.na(FU2_R_GENDER))&(SEX_DB=="(1) Male")) ~ "Most",


 ((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (is.na(FU2_R_GENDER))&(SEX_DB=="(2) Female")) ~ "Most",
 
((is.na(FU2_R_GENDER)) & (is.na(BL_R_GENDER)) & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(1)Male")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(BL_R_GENDER)) & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(2)Female")) ~ "Most",

((FU2_R_GENDER=="(1) Male") & (BL_R_GENDER
=="(1) Male") & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(1)Male")) ~ "More",

((FU2_R_GENDER=="(2) Female") & (BL_R_GENDER
=="(2) Female") & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(2) Female")) ~ "More",

((FU2_R_GENDER=="(2) Female") & (is.na(BL_R_GENDER)) & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2) Female")) ~ "Least",

((FU2_R_GENDER=="(1) Male") & (is.na(BL_R_GENDER)) & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1) Male")) ~ "Least",

((FU2_R_GENDER=="(1) Male") & (BL_R_GENDER=="(1) Male")  & (SEX_DB=="(1) Male")& (is.na(FU1_R_GENDER))) ~ "Least",

((FU2_R_GENDER=="(2) Female") & (BL_R_GENDER
=="(2) Female")  & (SEX_DB=="(2) Female")& (is.na(FU1_R_GENDER))) ~ "Least",

((is.na(FU2_R_GENDER)) & (BL_R_GENDER
=="(1) Male")  & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1) Male")) ~ "Most",

(is.na(FU2_R_GENDER) & (BL_R_GENDER
=="(2) Female")  & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2) Female")) ~ "Most",

#(SEX_DB=="(3) Unknown") ~ "More",

#(BL_R_GENDER==NA)~ "Least",

#(FU1_R_GENDER==NA)~ "Least",

#(FU2_R_GENDER==NA)~ "Most",

   
    (TRUE)~ "No"
))

new_df1%>%select(weights,SEX_DB,FU1_R_GENDER,BL_R_GENDER,FU2_R_GENDER)

```

```{r}

new_df2 <- (new_df1) %>% 
mutate(Transition = case_when(
  
  ((SEX_DB=="(1) Male") & ((BL_R_GENDER
!=NA)|(BL_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((BL_R_GENDER
!=NA)|(BL_R_GENDER!="(2) Female"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(2) Female"))) ~ "Yes",

 ((SEX_DB=="(1) Male") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

((BL_R_GENDER=="(1) Male") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(1) Male"))) ~ "Yes",

((BL_R_GENDER=="(2) Female") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(2) Female"))) ~ "Yes",

((BL_R_GENDER=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((BL_R_GENDER=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

((FU1_R_GENDER=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((FU1_R_GENDER=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

(TRUE)~ "No"
))

new_df2%>%select(Transition)%>%filter(Transition=="No")

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_SEESTMWO), fill = FU1_SEESTMWO, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights | I feel I am
  a person of worth,
  the equal of other people.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_SEESTMWO), fill = BL_SEESTMWO, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| I feel I 
       am a person of worth,the equal 
       of other people.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_LCGETAHD), fill = FU1_LCGETAHD, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| Every time I try 
       to get ahead, something or 
       somebody stops me.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_LCGETAHD), fill = BL_LCGETAHD, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  
  labs(title='(weights| Every time I try 
       to get ahead, something or 
       somebody stops me.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_SESATISF), fill = FU1_SESATISF, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights|On the whole I am
  satisfied with myself.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_SESATISF), fill = BL_SESATISF, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights|On the whole I am
  satisfied with myself.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_GLEADER), fill = FU1_GLEADER, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| During this school 
  year,have you held a campus 
  leadership position?)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_GLEADER), fill = BL_GLEADER, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| During this school
            year,have you held a campus 
              leadership position?)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_UDIFFFRN), fill = BL_UDIFFFRN, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| How difficult did
       you find making friends?)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_LCGETAHD), fill = FU1_LCGETAHD, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| Every time I try
       to get ahead, something or
       somebody stops me.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_LCGETAHD), fill = BL_LCGETAHD, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| Every time I try
       to get ahead, something or
       somebody stops me.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_FRNNCOLL), fill = BL_FRNNCOLL, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| Most of my 
       friends are not in college?)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(FU1_SEDOWELL), fill = FU1_SEDOWELL, check_overlap = TRUE,
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights|I am able to do
  things as well as most other
  people.)')


```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_SEDOWELL), fill = BL_SEDOWELL, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  ggtitle('(weights|I am able to do
  things as well as most other 
  people.)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_SENOGOOD), fill = BL_SENOGOOD, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights|At times, I think
              I am not good at all)')
```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_LCPLANSW), fill = BL_LCPLANSW, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights|When I make plans,
               I am almost certain I can
               make them work.
)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_COMDEGRE), fill = BL_COMDEGRE, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=5, hjust= .1))+
  labs(title='(weights| I am committed 
            to earning a degree at 
       my current college or university.
)')

```

```{r}
ggplot(data = new_df1) +
  geom_mosaic(aes(x=product(BL_UNDSOSTU), fill = BL_UNDSOSTU, 
                  conds = product(weights))) +
   theme(axis.text.x=element_text(angle=-25, hjust= .1))+theme(axis.text.y=element_text(angle=0, hjust= .1))+
  labs(title='f(unknown sex |Since entering 
            college or a university, to 
        what extent have you turned to other 
       students for support and encouragement? 
)')

```
