---
title: "pre processing"
output: html_document
date: '2022-08-01'
---

```{r}
library(dplyr)
library(ggplot2)
library(ggmosaic)
```

#1 Participation ID for participants who took part in all three surveys

```{r}
all_three=(da34375.0001) %>% filter(FU1_MARKER=="(1) Completed Wave",FU2_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% select(SU_ID)

all_three

```

#2 Participation ID for participants who took part in baseline and first follow up survey

```{r}
first_two=(da34375.0001) %>% filter(FU1_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% select(SU_ID)

first_two
```

#3 Participation ID for participants who took part in baseline and second follow up.

```{r}
first_last=(da34375.0001) %>% filter(FU2_MARKER=="(1) Completed Wave", BL_MARKER=="(1) Completed Wave")%>% mutate(Participation=c("First and Last"))%>%select(SU_ID,participation)

first_last
```

#4 Participation ID for participants who took part in first follow up and second follow up.

```{r}
second_last=(da34375.0001) %>% filter(FU1_MARKER=="(1) Completed Wave", FU2_MARKER=="(1) Completed Wave")%>% mutate(participation=c("second and last"))%>%select(SU_ID,participation)

second_last
```


#4 Creating a newdata set consisting of all columns from the original dataset along with a new "participation" column which tracks if the participant participated in "all three","first and last", "first two" or NA.

```{r}
df <- da34375.0001 %>% 
mutate(Participation = case_when(
  
  ((FU2_MARKER=="(1) Completed Wave") & (BL_MARKER=="(1) Completed Wave")&(FU1_MARKER=="(1) Completed Wave")) ~ "All Three",

    ((FU2_MARKER=="(1) Completed Wave") & (BL_MARKER=="(1) Completed Wave")&(FU1_MARKER=="(0) Did not complete")) ~ "First and Last",
   
    
    
    ((BL_MARKER=="(1) Completed Wave")&(FU1_MARKER=="(1) Completed Wave")&(FU2_MARKER=="(0) Did not complete")) ~ "First Two",

   ((BL_MARKER=="(0) Did not complete")&(FU1_MARKER=="(1) Completed Wave")&(FU2_MARKER=="(1) Completed Wave")) ~ "Second and Last",
  
  TRUE~"NO"

  
  
))

df
```

#5 Check to see code #4 works accurately

```{r}
new<-df%>%select(Participation,SU_ID,BL_MARKER,FU1_MARKER,FU2_MARKER)
new
```

#6 Filtering for "participation" column with"all three","first and last", "first two"

```{r}
new_dataset<- df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SU_ID, SEX_DB,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)%>%filter(SEX_DB=="(1) Male" & BL_R_GENDER=="(2) Female")
 
new_dataset

```

#filtering m to f and f to m participants

```{r}
new_df <- (da34375.0001) %>% 
mutate(transition = case_when(
  
  ((SEX_DB=="(1) Male") & (BL_R_GENDER
=="(2) Female")) ~ "MtoF",

   ((SEX_DB=="(2) Female") & (BL_R_GENDER
=="(2) Male")) ~ "FtoM",
 
   
    (TRUE)~ "No"
))
new_df%>%select(transition)%>%filter(transition!="No")
```

#Looking for missing data
```{r}
new_dataset_1<- df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SEX_DB,SU_ID)%>%filter(SEX_DB!="(1) Male" & SEX_DB!="(2) Female")
 
new_dataset_1

```
#From the filtered dataset identifying participants whose sex at birth is reported male
```{r}
new_dataset_2<- df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SU_ID,SEX_DB)%>%filter(SEX_DB=="(1) Male")

new_dataset_2
```

#From the filtered dataset identifying participants whose sex at birth is reported male
```{r}
new_dataset_3<- df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SU_ID,SEX_DB)%>%filter(SEX_DB=="(2) Female")

new_dataset_3
```
 
#Selecting columns based on variables of interest

```{r}
filtered_dataset<- df%>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SU_ID,SEX_DB,BL_R_GENDER,BL_GMSLEADR,BL_GMSLDACT,BL_FRNNCOLL,BL_GLEADER, BL_UDIFFFRN,BL_SESATISF,BL_LCGETAHD,BL_SEESTMWO,BL_SEDOWELL,BL_SEUSELES,BL_SENOGOOD,BL_LCPLANSW,BL_COMDEGRE,BL_UDIFFSCW,BL_UDIFFTIM,BL_UNDSOSTU, BL_SELFGOOD,BL_UDIFFFRN,BL_UNDSFAC,BL_UNDSOSTU,BL_LCNECNTR,BL_HSMATHYR,BL_HSSCIEYR,FU1_GMSLEADR,FU1_GLEADER,FU1_R_GENDER,FU1_APLYGRAD,FU1_GMSLDACT,FU1_UCULTURE,FU1_GLEADER,FU1_RGRPSSUP,FU1_POLPROG,FU1_DIFFSCHW,FU1_PPOTHR,FU1_DIFFSCHW,FU1_SOCDISCR,FU1_FACINAPP,FU1_SELFGOOD,FU1_LCNECNTR,FU1_SEESTMWO,FU1_SEDOWELL,FU1_LCGETAHD,FU1_AENOTWEL,FU1_AEMAKCOL,FU1_SESATISF,FU1_SEUSELES,FU1_SENPROUD,FU2_NOGRNOSC,FU2_GMSLDACT,FU2_HLTHINSR,FU2_SATCOWRK,FU2_OPPJOB,FU2_COMDIVRS,FU2_PNSADJUS,FU2_DESTLEAD,FU2_POSCULT,FU2_DIFFVIEW,FU2_BULDCOAL,FU2_VOTEELEC,FU2_PROMEQIT,FU2_R_GENDER,FU2_GMSLEADR)
#%>%filter(SEX_DB=="(2) Female")

filtered_dataset
```

# Identifying columns with not all "male" or "female" values for sex at birth and gender variable. Identifying missing values.

```{r}
new_dataset_7<- df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SEX_DB,SU_ID,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)%>%filter((SEX_DB=="(1) Male"&BL_R_GENDER=="(1) Male"&FU1_R_GENDER=="(1) Male"&FU2_R_GENDER=="(1) Male")|(SEX_DB=="(2) Female"&BL_R_GENDER=="(2) Female"&FU1_R_GENDER=="(2) Female"&FU2_R_GENDER=="(2) Female"))
 
new_dataset_7

```

# Using the new dataset created prior to this to identify participants with atleast one of sex nad gender variable missing
```{r}
l<-df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SEX_DB,SU_ID,BL_R_GENDER,FU1_R_GENDER,FU2_R_GENDER)

new_df<-anti_join(l,new_dataset_7,by="SU_ID")
new_df

```

#Adding a new column that identifies participants when atleast one of sex and gender variable is missing

```{r}
new_df <- df %>% 
mutate(unknown_sex = case_when(
  
  ((SEX_DB!="(1) Male") & (SEX_DB!="(2) Female"))~ "YES",
   
   TRUE~"NO"))

new_df

```

#Selecting variables of interest for data visualization
```{r}
missing<- new_df %>%filter(Participation=="All Three"|Participation=="First and Last"|Participation=="First Two"|Participation=="Second and Last")%>%select(SU_ID,SEX_DB,BL_GMSLEADR,BL_GMSLDACT,BL_FRNNCOLL,BL_GLEADER,BL_UDIFFFRN,BL_SESATISF,BL_LCGETAHD,BL_SEESTMWO,BL_SEDOWELL,BL_SEUSELES,unknown_sex,BL_SENOGOOD,BL_LCPLANSW,BL_COMDEGRE,BL_UDIFFSCW,BL_UDIFFTIM,BL_UNDSOSTU, BL_SELFGOOD)

missing
```

# Assigning likelihood of participants based on missing sex and gender variable in initial, baseline, first follow up, and second follow up study 

```{r}
new_df1 <- (filtered_dataset) %>% 
mutate(weights = case_when(
  
  ((SEX_DB=="(3) Unknown") & (is.na(BL_R_GENDER)
) & (FU1_R_GENDER=="(2) Female")& (FU2_R_GENDER=="(2) Female")) ~ "Most",

((SEX_DB=="(3) Unknown") & (is.na(BL_R_GENDER)) & (FU1_R_GENDER=="(1) Male")& (FU2_R_GENDER=="(1) Male")) ~ "Most",

   ((SEX_DB=="(3) Unknown") & (is.na(FU1_R_GENDER)) &(BL_R_GENDER=="(1) Male")&(FU2_R_GENDER=="(1) Male")) ~ "Least",

 ((SEX_DB=="(3) Unknown") & (is.na(FU1_R_GENDER)) &(BL_R_GENDER=="(2)Female")&(FU2_R_GENDER=="(2) Female")) ~ "Least",

((SEX_DB=="(3) Unknown") & (is.na(FU2_R_GENDER))& (FU1_R_GENDER=="(1)Male")&(BL_R_GENDER=="(1)Male")) ~ "Most",

((SEX_DB=="(3) Unknown") & (is.na(FU2_R_GENDER))& (FU1_R_GENDER=="(2)Female")&(BL_R_GENDER=="(2)Female")) ~ "Most",


((is.na(BL_R_GENDER)) & (is.na(FU2_R_GENDER)) & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1)Male")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU2_R_GENDER)) & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2)Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(1) Male")&(FU2_R_GENDER=="(1) Male")) ~ "Least",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(2)Female")&(FU2_R_GENDER=="(2) Female")) ~ "Least",
 
 
((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(2) Female")&(BL_R_GENDER=="(2) Female")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER))&(SEX_DB=="(1) Male")&(BL_R_GENDER=="(1) Male")) ~ "Most",
 
 
((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(BL_R_GENDER=="(1) Male")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(BL_R_GENDER=="(2) Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(FU2_R_GENDER=="(2) Female")) ~ "Most",

((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (SEX_DB=="(3) Unknown")&(FU2_R_GENDER=="(1) Male")) ~ "Most",

 
 ((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (is.na(FU2_R_GENDER))&(SEX_DB=="(1) Male")) ~ "Most",


 ((is.na(BL_R_GENDER)) & (is.na(FU1_R_GENDER)) & (is.na(FU2_R_GENDER))&(SEX_DB=="(2) Female")) ~ "Most",
 
((is.na(FU2_R_GENDER)) & (is.na(BL_R_GENDER)) & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(1)Male")) ~ "Most",

((is.na(FU2_R_GENDER)) & (is.na(BL_R_GENDER)) & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(2)Female")) ~ "Most",

((FU2_R_GENDER=="(1) Male") & (BL_R_GENDER
=="(1) Male") & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(1)Male")) ~ "Most",

((FU2_R_GENDER=="(2) Female") & (BL_R_GENDER
=="(2) Female") & (SEX_DB=="(3) Unknown")& (FU1_R_GENDER=="(2) Female")) ~ "Most",

((FU2_R_GENDER=="(2) Female") & (is.na(BL_R_GENDER)) & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2) Female")) ~ "Least",

((FU2_R_GENDER=="(1) Male") & (is.na(BL_R_GENDER)) & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1) Male")) ~ "Least",

((FU2_R_GENDER=="(1) Male") & (BL_R_GENDER=="(1) Male")  & (SEX_DB=="(1) Male")& (is.na(FU1_R_GENDER))) ~ "Least",

((FU2_R_GENDER=="(2) Female") & (BL_R_GENDER
=="(2) Female")  & (SEX_DB=="(2) Female")& (is.na(FU1_R_GENDER))) ~ "Least",

((is.na(FU2_R_GENDER)) & (BL_R_GENDER
=="(1) Male")  & (SEX_DB=="(1) Male")& (FU1_R_GENDER=="(1) Male")) ~ "Most",

(is.na(FU2_R_GENDER) & (BL_R_GENDER
=="(2) Female")  & (SEX_DB=="(2) Female")& (FU1_R_GENDER=="(2) Female")) ~ "Most",

#(SEX_DB=="(3) Unknown") ~ "More",


   
    (TRUE)~ "No"
))

new_df1%>%select(weights,SEX_DB,FU1_R_GENDER,BL_R_GENDER,FU2_R_GENDER)

```

# Identifying participants who have transitioned from male to female or female to male
```{r}

new_df2 <- (new_df1) %>% 
mutate(Transition = case_when(
  
  ((SEX_DB=="(1) Male") & ((BL_R_GENDER
!=NA)|(BL_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((BL_R_GENDER
!=NA)|(BL_R_GENDER!="(2) Female"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(2) Female"))) ~ "Yes",

 ((SEX_DB=="(1) Male") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((SEX_DB=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

((BL_R_GENDER=="(1) Male") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(1) Male"))) ~ "Yes",

((BL_R_GENDER=="(2) Female") & ((FU1_R_GENDER
!=NA)|(FU1_R_GENDER!="(2) Female"))) ~ "Yes",

((BL_R_GENDER=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((BL_R_GENDER=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

((FU1_R_GENDER=="(1) Male") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(1) Male"))) ~ "Yes",

((FU1_R_GENDER=="(2) Female") & ((FU2_R_GENDER
!=NA)|(FU2_R_GENDER!="(2) Female"))) ~ "Yes",

(TRUE)~ "No"
))

new_df2%>%select(Transition)%>%filter(Transition=="No")

```


